Hector Permafrost

### 2020-01-23 analysis/paper/paper.Rmd
Show permafrost frozen fraction output

run_rcp <- function(rcp) {
  inidir <- file.path("~", "Projects", "hector_project",
                      "hector-permafrost-submodel", "inst", "input")
  inifile <- normalizePath(file.path(inidir, paste0("hector_rcp", rcp, ".ini")))
  stopifnot(file.exists(inifile))
  hc <- newcore(inifile)
  dates <- seq(1750, 2100)
  run(hc, max(dates))
  outvars <- c(ATMOSPHERIC_CO2(), GLOBAL_TEMP(), PERMAFROST_C(), SOIL_C())
  no_pf <- fetchvars(hc, dates, outvars, scenario = "Original")
  reset(hc)
  setvar(hc, 0, PERMAFROST_C(), 1035, "PgC")
  run(hc, max(dates))
  yes_pf <- fetchvars(hc, dates, outvars, scenario = "Permafrost")
  return(tibble::as_tibble(dplyr::bind_rows(no_pf, yes_pf)))
}

@@

results %>%
  mutate(variable = recode(
    variable,
    Ca = "Atmospheric CO2 (ppm)",
    Tgav = "Global mean temperature anomaly (K)",
    permafrost_c = "Permafrost C pool (PgC)",
    soil_c = "Soil C pool (PgC)"
  )) %>%
  ggplot() +
  aes(x = year, y = value, linetype = scenario, color = RCP) +
  geom_line() +
  facet_wrap(vars(variable), scales = "free_y") +
  theme_bw() +
  theme(axis.title = element_blank())

>>>>

run_rcp <- function(rcp) {
  inidir <- file.path("~", "Projects", "hector_project",
                      "hector-permafrost-submodel", "inst", "input")
  inifile <- normalizePath(file.path(inidir, paste0("hector_rcp", rcp, ".ini")))
  stopifnot(file.exists(inifile))
  hc <- newcore(inifile)
  dates <- seq(1750, 2100)
  run(hc, max(dates))
  outvars <- c(ATMOSPHERIC_CO2(), GLOBAL_TEMP(), "f_frozen", SOIL_C())
  no_pf <- fetchvars(hc, dates, outvars, scenario = "Original")
  reset(hc)
  setvar(hc, 0, PERMAFROST_C(), 1035, "PgC")
  run(hc, max(dates))
  yes_pf <- fetchvars(hc, dates, outvars, scenario = "Permafrost")
  return(tibble::as_tibble(dplyr::bind_rows(no_pf, yes_pf)))
}

@@

results %>%
  mutate(variable = recode_factor(
    variable,
    Tgav = "Global mean temperature anomaly (K)",
    Ca = "Atmospheric CO2 (ppm)",
    soil_c = "Active soil C pool (PgC)",
    permafrost_c = "Permafrost C pool (PgC)",
    f_frozen = "Frozen permafrost fraction"
  )) %>%
  ggplot() +
  aes(x = year, y = value, linetype = scenario, color = RCP) +
  geom_line() +
  facet_wrap(vars(variable), scales = "free_y") +
  theme_bw() +
  theme(axis.title = element_blank())
